Test Document

### 2024-11-28 paper.Rmd
added colours

---
title: "The Gillespie Algorithm: Stochastic Modeling of Molecular Reaction Networks"
author: 
  - Jiayu Guo
  - Sinan Ma 
  - Anna Szydlowski
date: "`r Sys.Date()`"
abstract: "The Gillespie Algorithm provides a robust framework for simulating stochastic molecular reaction networks, capturing the inherent randomness of chemical and biochemical processes. Unlike deterministic methods, the algorithm accurately models systems with low molecular counts, where fluctuations significantly influence reaction dynamics. This project explores the theoretical foundation of the Gillespie Algorithm, including its basis in the master equation, and demonstrates its application in simulating two molecular systems: the photodimerization of thymine, a process linked to UV-induced DNA damage, and the radioactive decay of isotopes. Through these simulations, the algorithm's capability to model stochastic trajectories is highlighted, offering insights into reaction mechanisms and the role of randomness in molecular processes. The implications of these findings extend to a variety of disciplines, including molecular biology, environmental monitoring, and nuclear medicine."
output:
  pdf_document:
    number_sections: true
    citation_package: biblatex
spacing: double
header-includes:
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}
  - \fancyhead[L]{The Gillespie Algorithm}
  - \fancyfoot[CO,CE]{}
  - \fancyfoot[LE,RO]{\thepage}
  - \usepackage{setspace}
  - \doublespacing
  - \usepackage{xcolor} 
  - \usepackage{hyperref}
  - \hypersetup{colorlinks = true, linkcolor = blue}

>>>>

---
title: "The Gillespie Algorithm: Stochastic Modeling of Molecular Reaction Networks"
author: 
  - Jiayu Guo
  - Sinan Ma 
  - Anna Szydlowski
date: "`r Sys.Date()`"
abstract: "The Gillespie Algorithm provides a robust framework for simulating stochastic molecular reaction networks, capturing the inherent randomness of chemical and biochemical processes. Unlike deterministic methods, the algorithm accurately models systems with low molecular counts, where fluctuations significantly influence reaction dynamics. This project explores the theoretical foundation of the Gillespie Algorithm, including its basis in the master equation, and demonstrates its application in simulating two molecular systems: the photodimerization of thymine, a process linked to UV-induced DNA damage, and the radioactive decay of isotopes. Through these simulations, the algorithm's capability to model stochastic trajectories is highlighted, offering insights into reaction mechanisms and the role of randomness in molecular processes. The implications of these findings extend to a variety of disciplines, including molecular biology, environmental monitoring, and nuclear medicine."
output:
  pdf_document:
    number_sections: true
    citation_package: biblatex
linkcolor: blue
urlcolor: blue
spacing: double
header-includes:
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}
  - \fancyhead[L]{The Gillespie Algorithm}
  - \fancyfoot[CO,CE]{}
  - \fancyfoot[LE,RO]{\thepage}
  - \usepackage{setspace}
  - \doublespacing

### 2024-11-28 test.Rmd
added colours

---
title: "Test Document"
output:
  pdf_document:
    keep_tex: true
header-includes:
  - \usepackage{xcolor}
  - \usepackage{hyperref}
  - \hypersetup{colorlinks=true, linkcolor=red, citecolor=green, urlcolor=blue}
---

>>>>

---
title: "Test Document"
output:
  pdf_document:
    latex_engine: xelatex
    keep_tex: true
    number_sections: true
    citation_package: biblatex
linkcolor: blue
spacing: double
header-includes:
  - \AtBeginDocument{\hypersetup{colorlinks=true,linkcolor=blue,filecolor=magenta,urlcolor=cyan}}
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}
  - \fancyhead[L]{The Gillespie Algorithm}
  - \fancyfoot[CO,CE]{}
  - \fancyfoot[LE,RO]{\thepage}
  - \usepackage{setspace}
  - \doublespacing
  - \PassOptionsToPackage{hyphens}{url}  % Ensure URLs are broken correctly
  - \usepackage{xcolor} 
  - \usepackage{hyperref}
  - \hypersetup{colorlinks=true,linkcolor=blue,filecolor=magenta,urlcolor=cyan}
---
